Stability and Chaos in Multi-Agent Reinforcement Learning

### 2021-03-27 Documents/ChaoticDynamics/IJCAI 2021/response/ijcai21-authors-response.tex
removed binaries

@@

The reviewer makes a pertinent point regarding the model chosen for the analysis. Indeed our
analysis is of an iterated normal-form game, which has a strong history in the learning community.
The state of the art regarding evolutionary game theoretic analysis of learning processes is not yet
at a stage where multi-stage games, or continuous state spaces can be accurately analysed and,
indeed, we remark in the conclusion that, as EGT models are improved to capture such complex games 
(such as with active environments or heterogeneous agents), we must analyse those models to
understand their implications for the stability and behaviour of learning algorithms such as
Q-Learning. This is a point for future work which we consider.

@@

@@

Regarding the analysis of other reinforcement learning algorithms, we definitely believe that this
is an important and interesting line of inquiry. We mention in our conclusion that, as
dynamical models are developed for the algorithms you mention, analyses such as the present work
will help provide insight into what they predict regarding the stabilty and behaviour of those
algorithms.
% paragraph reviewer_65 (end)

>>>>

\usepackage{color}
\newcommand\fb[1]{\textcolor{red}{FB: #1}}

@@

\fb{the first paragraph can be reduced if we need space.}
The reviewer makes a pertinent point regarding the model chosen for the analysis. Indeed our
analysis is of an iterated normal-form game, which has a strong history in the learning community.
The state of the art regarding evolutionary game theoretic analysis of learning processes is not yet
at a stage where multi-stage games, or continuous state spaces can be accurately analysed and,
indeed, we remark in the conclusion that, as EGT models are improved to capture such complex games 
(such as with active environments or heterogeneous agents), we must analyse those models to
understand their implications for the stability and behaviour of learning algorithms such as
Q-Learning. This is a point for future work which we consider.

\fb{what you write is fine, but I'd stress even further the difference and elements of novelty wrt SOTA.}

@@

\fb{we could stress even further that taking $\Gamma$ to average over a certain type of reward is completely standard in the literature.}

@@

Regarding the analysis of other reinforcement learning algorithms, we definitely believe that this
is an important and interesting line of inquiry, \fb{but far beyond the scope of the current contribution}. We mention in our conclusion that, as
dynamical models are developed for the algorithms you mention, analyses such as the present work
will help provide insight into what they predict regarding the stability and behaviour of those
algorithms.
% paragraph reviewer_65 (end)
